RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

>>>>

#### Correlation between individuals
```{r corr.btw.indivs}
form = ~ (1|CellType) + (1|Batch) + (1|Individual.ID) 
vobj.simple = voomWithDreamWeights(dge, form, info, BPPARAM=SnowParam(12, progressbar=TRUE))

# fit.simple = dream(vobj.simple, form, info, BPPARAM=SnowParam(12, progressbar=TRUE))
# residCompare = residuals(fit.simple)

residCompare = fitVarPartModel(vobj.simple, form, info, fxn=function(fit){
  library(lme4)  
  fit@resp[['y']] - variancePartition::get_prediction(fit, ~ (1|CellType) + (1|Batch))
}, BPPARAM=SnowParam(12, progressbar=TRUE))

residCompare = do.call(rbind, residCompare)
```

```{r plot_within_btw}
plot_within_btw = function( simMat, design, col=c("lightblue", "lightgreen"),main='',ylim=NULL,...){
  variation = list(type=c(), value=c(), donor1=c(), donor2=c())
  for(i in 1:ncol(design)){
    idx1 = which(design[,i] == 1)   
    idx0 = which(design[,i] == 0)
    C_sub = simMat[idx1, idx1]
    variation$type = append( variation$type, rep("Same Donor", sum(lower.tri(C_sub))) )  
    variation$value = append( variation$value, C_sub[lower.tri(C_sub)])   
    variation$donor1 = append(variation$donor1, rep(colnames(design)[i], length(C_sub[lower.tri(C_sub)]) ))      
    variation$donor2 = append(variation$donor2, rep(colnames(design)[i], length(C_sub[lower.tri(C_sub)]) ))
    variation$type = append( variation$type, rep("Different Donor", length(simMat[idx1,idx0])) )  
    variation$value = append( variation$value, simMat[idx1,idx0])    
    variation$donor1 = append(variation$donor1, rep("", length(simMat[idx1,idx0])) )      
    variation$donor2 = append(variation$donor2, rep("", length(simMat[idx1,idx0])))
  }
  variation = as.data.frame(variation)
  fig = ggplot( variation, aes(type, value)) + geom_violin(scale = "width", aes(fill=type)) + 
    ylab("Variance explained (%)") + xlab("") + geom_boxplot(width = 0.07, 
        fill = "grey", outlier.color = "black") + theme_bw(15) + 
        scale_fill_manual(values = col) + theme(legend.position = "none") + 
        ylab("Correlation between samples") + scale_fill_manual(values=c("grey", "steelblue1"))
    if( main !='' ){
      fig = fig + ggtitle( main )
    }
    if( !is.null(ylim) ){
      fig = fig + ylim( ylim )
    }
    fig = fig + theme(aspect.ratio=1)
    return(list(fig=fig, variation=variation))
}

C = cor( residCompare, method="spearman" )

res = plot_within_btw( C, model.matrix(~Individual.ID+0, info)) 
res$fig
```
